%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}

Each chapter of this dissertation has a corresponding 
research paper.  
I have collaborated with my supervisor, Prof. Ali Mesbah, for 
conducting the research projects in all chapters. 
I was the first author and main contributor for all papers, 
including formulating the idea, design and development of the 
approach, and evaluation of the work. I had the collaboration 
of Andrea Stocco in \autoref{chp:survey} and Davood Mazinanian in Chapters \ref{chp:survey} and  \ref{chp:maintainability}, 
both of whom are former post-doctoral fellows in our lab. 
The papers for each chapter are as follows:

\begin{itemize}
	\item \autoref{chp:survey}: 
		\begin{itemize}
		\item A survey on the use of computer vision to improve software engineering tasks~\cite{bajammal2020survey}, repo:~\cite{tse-repo}. Mohammad Bajammal, Andrea Stocco, Davood Mazinanian, and Ali Mesbah. Accepted in IEEE Transactions on Software Engineering (TSE) 2020.
	\end{itemize}
	
	
	\item \autoref{chp:testability}: 
		\begin{itemize}
		\item Web canvas testing through visual inference~\cite{canvas_icst2018}, repo:~\cite{icst-repo}. 
		Mohammad Bajammal and Ali Mesbah. 
		Proceedings of the International Conference on Software Testing, Verification and Validation (ICST) 2018. Distinguished paper award.
	\end{itemize}
	
	
	\item \autoref{chp:accessibility_testing}: 
		\begin{itemize}
		\item Semantic Web Accessibility Testing via Hierarchical Visual Analysis~\cite{bajammal2021semantic}, repo:~\cite{icse-repo}. 
		Mohammad Bajammal and Ali Mesbah. 
		Proceedings of the ACM/IEEE International Conference on Software Engineering (ICSE) 2021. 
	\end{itemize}
	

	\item \autoref{chp:accessibility_repair}: 
		\begin{itemize}
		\item Automated web form accessibility labeling using visual cues. Mohammad Bajammal and Ali Mesbah. Under submission to an upcoming software engineering venue.  
	\end{itemize}
	

	\item \autoref{chp:maintainability}: 
	\begin{itemize}
		\item Generating reusable web components from mockups~\cite{bajammal2018generating}, repo:~\cite{ase-repo}.. 
		Mohammad Bajammal, Davood Mazinanian, and Ali Mesbah. 
		Proceedings of the IEEE/ACM International Conference on Automated Software Engineering (ASE) 2018. 
	\end{itemize}

\end{itemize} 

In addition, I have worked on the following projects but they were not included in this dissertation as they are outside 
the scope of the dissertation. 

\noindent
- Style-Guided Web Application Exploration. Davood Mazinanian, Mohammad Bajammal, Ali Mesbah. arXiv:2111.12184 (2021). \\ 
- Page Segmentation using Visual Adjacency Analysis. Mohammad Bajammal, Ali Mesbah.  arXiv:2112.11975 (2021).  
